Using an SMT engine to generate Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-18 2017-Xudong-SMT/ActaInformatica.tex
Inserted FailureTimerv2-2 and its results.

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{ActaXFIG/BIPspec-ArchFailureTimer-v2-1a}
  \caption{The BIP specification of the Failure Monitor architecture}
  \label{schema:ArchFailure:BIP}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.9\columnwidth]{ActaXFIG/FailureTimerPNET-v2-1a}
  \caption{pNet encoding of the Failure Monitor architecture}
  \label{schema:ArchFailure:pNet}
\end{figure}

@@

For this example, the tool (using Algorithm 1) builds 218 open transitions, whereof 206
are detected unsatisfiable by Z3.  The resulting open automaton, with
4 reachable global states (out of the possible 6) and 12 open
transitions, is shown in Fig.~\ref{schema:resultOA1}.

\begin{figure}[t]
  \centerline{\includegraphics[width=12cm]{ActaXFIG/FailureTimerOA-v2-1a}}
  \caption{Open Automaton for the Failure Monitor architecture}
  \label{schema:resultOA1}
\end{figure}

@@

Failure Monitor enforces 1)~the safety property \emph{``the
  system reset never happens, unless asked for by a timeout
  following a failure''}, formalised in CTL by
%
\[
\varphi \land \mathtt{AG} (\PortReset \rightarrow \varphi),
\quad\text{where}\
%
\varphi = \mathtt{A} [\lnot \PortReset\ \mathtt{W}\ \PortAsk]
\land \mathtt{A} [\lnot \PortAsk\ \mathtt{W}\ \PortFail],
\]
%
($\mathtt{W}$ being the \emph{weak until} operator) and 2)~the
liveness property \emph{``a reset will be fired when asked for by
  a timeout''}:
%
$\mathtt{AG}(\PortAsk \rightarrow \mathtt{AF}\ \PortReset)$.
%
The satisfaction of the safety property could be established by
applying symbolic model checking techniques.  However, in this
example, it is obvious by inspection of the open automaton.  The
satisfaction of the liveness property relies on the above observation
that in the state $\ostate{s2,t0}$ only the reset transition involves
$\NameCtrl$.  Therefore, under resonable scheduling assumptions,
$\PortReset$ will always be fired.

@@

\subsection{Composing 2 FailureTimer BIP Architecture}
\noteInEM{Modifications stopped here}
\label{section:resultTimerInterval}
\TODO{Enhanced FailureTimer, 2 instances composed, with duplicated control and Timer}

\begin{figure}[t]
  \centering
  \includegraphics[width=0.9\columnwidth]{XFIG/FailureTimerPNET-v4}
  \caption{The open pNet encoding the Failure Monitor architecture (\ref{fig:schema:ArchFailure:BIP}) without the Max Progress priority model}
  \label{fig:FailureTimer:pNet}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{ActaXFIG/BIPspec-ArchFailureTimer-v2-2}
  \caption{The BIP specification of the Failure Monitor architecture}
  \label{schema:ArchFailure:BIP}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.9\columnwidth]{ActaXFIG/FailureTimerPNET-v2-2}
  \caption{pNet encoding of the Failure Monitor architecture}
  \label{schema:ArchFailure:pNet}
\end{figure}

@@

For this example, the tool (using Algorithm 1) builds 258 open transitions, whereof 248
are detected unsatisfiable by Z3.  The resulting open automaton, with
3 reachable global states (out of the possible 6) and 10 open
transitions, is shown in Fig.~\ref{schema:resultOA1}.

\begin{figure}[t]
  \centerline{\includegraphics[width=12cm]{ActaXFIG/FailureTimerOA-v2-2}}
  \caption{Open Automaton for the Failure Monitor architecture}
  \label{schema:resultOA1}
\end{figure}

@@

Failure Monitor enforces \noteEM{NO!!!}1)~the safety property \emph{``the
  system reset never happens, unless asked for by a timeout
  following a failure''}, formalised in CTL by
%
\[
\varphi \land \mathtt{AG} (\PortReset \rightarrow \varphi),
\quad\text{where}\
%
\varphi = \mathtt{A} [\lnot \PortReset\ \mathtt{W}\ \PortAsk]
\land \mathtt{A} [\lnot \PortAsk\ \mathtt{W}\ \PortFail],
\]
%
($\mathtt{W}$ being the \emph{weak until} operator) and 2)~the
liveness property \emph{``a reset will be fired when asked for by
  a timeout''}:
%
$\mathtt{AG}(\PortAsk \rightarrow \mathtt{AF}\ \PortReset)$.
%
The satisfaction of the safety property could be established by
applying symbolic model checking techniques.  However, in this
example, it is obvious by inspection of the open automaton.  The
satisfaction of the liveness property relies on the above observation
that in the state $\ostate{s2,t0}$ only the reset transition involves
$\NameCtrl$.  Therefore, under resonable scheduling assumptions,
$\PortReset$ will always be fired.

@@

\subsection{Composing 2 FailureTimer BIP Architectures}
\noteInEM{Modifications stopped here}
\label{section:resultTimerInterval}
\TODO{Enhanced FailureTimer, 2 instances composed, with duplicated control and Timer}

\begin{figure}[t]
  \centering
  \includegraphics[width=0.9\columnwidth]{ActaXFIG/FailureTimerPNET-v2-2}
  \caption{The open pNet encoding the Failure Monitor architecture (\ref{fig:schema:ArchFailure:BIP})}
  \label{fig:FailureTimer:pNet}
\end{figure}
